\documentclass[12pt]{article}

\usepackage[T1]{fontenc}         % https://texfaq.org/FAQ-why-inp-font
\usepackage{fontawesome}         % icons
\usepackage{geometry}            % page dimensions
\usepackage{multicol}            % multi-column environments
\usepackage{textcomp}            % bullet symbol
\usepackage{tcolorbox}           % color boxes using tikz
\usepackage[explicit]{titlesec}  % formats for section headings
\usepackage{xcolor}              % color control, like green!20!white
\usepackage{hyperref}            % hyperlinks; this should be last

% Page dimensions
\geometry{
  left=0.6in,
  right=0.6in,
  top=0.4in,
  bottom=0.4in
}

% Define "\CC" as a command to typeset "C++" nicely
\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}

% Bullet style in bulleted lists
\renewcommand{\labelitemi}{\textopenbullet}

% Amount of space before paragraphs
\parskip 5pt

% Amount of space before and after a multicols environment
\multicolsep 5pt

% Don't indent the first line of a paragraph
\parindent 0pt

% No page numbers
\pagestyle{empty}

% Hyperlink configuration
\hypersetup{
  colorlinks=true,
  urlcolor=blue!80!black,
}

% Section header style (this behavior comes from the titlesec package)
\titleformat{\section} % the sectioning command to be redefined
            [hang] % shape
            {\sffamily\color{red}} % format to be applied
            {\thesection} % label
            {0pt} % sep
            {\Large #1} % before code
            [\titlerule{}] % after code

% Subsection header style (from titlesec)
\titleformat{\subsection} % the sectioning command to be redefined
            [hang] % shape
            {\large\bfseries} % format to be applied
            {\thesubsection} % label
            {0pt} % sep
            {\begin{tcolorbox}[nobeforeafter]#1\end{tcolorbox}}  % before code
            [] % after code

% Section spacing (moves sections 15pts into the left margin)
\titlespacing*{\section} % the sectioning command
              {-15pt} % left
              {0pt} % before-sep
              {5pt} % after-sep
              [0pt] % right-sep

% Subsection spacing
\titlespacing*{\subsection} % the sectioning command
              {0pt} % left
              {10pt} % before-sep
              {2pt} % after-sep
              [0pt] % right-sep

% Remove page number at bottom of page
\thispagestyle{empty}

% Adjust spacing in enumerate environment
\makeatletter
\AtBeginDocument {
  \renewcommand{\@listi} {
    \setlength{\itemsep}{0pt}
    \setlength{\parsep}{3pt}
    \setlength{\partopsep}{5pt}
    \setlength{\parskip}{0pt}
    \setlength{\topsep}{0pt}
    \setlength{\leftmargin}{30pt}
  }
  \renewcommand{\@listii} {
    \setlength{\itemsep}{5pt}
    \setlength{\topsep}{0pt}
  }
}
\makeatother

% Tag style (the green pillboxes used to list technologies)
\newtcbox{\tag}{
  on line,
  arc=7pt,
  boxrule=1pt,
  boxsep=0pt,
  top=2pt,
  bottom=2pt,
  left=6pt,
  right=6pt,
  before upper={\rule[-2pt]{0pt}{12pt}},
  colframe=green!50!black,
  colback=green!20!white}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
  {\sffamily\huge\textbf{Chris Clark}}
\end{center}

\tcbset{topbar/.style={
    frame empty,
    box align=top,
    width=(\linewidth-2mm)/2,
    nobeforeafter}}

% Note that "topbar" is a self-defined style defined with tcbset
\begin{tcolorbox}[
    topbar,
    boxsep=0pt,
    left=1pt,
    coltext=black!60,
    colback=white,
    halign=left,
    fontupper=\itshape\bfseries\large]

  I have a passion for programming, designing systems, and learning with people.
  I strive for simplicity and elegance. I help teams be productive through
  clarity, vision, and teamwork.

\end{tcolorbox}
\begin{tcolorbox}[
    topbar,
    left=1pt,
    colback=yellow!25!white]
  \begin{tabular}{r l}
    \faEnvelope\      & \texttt{cfclrk@gmail.com} \\
    \faPhone\         & \texttt{571-732-9827} \\
    \faGithub\        & \url{http://github.com/cfclrk} \\
    \faStackOverflow\ & \url{http://stackoverflow.com/u/340613} \\
    \faLinkedin\      & \url{http://linkedin.com/in/cfclrk} \\
  \end{tabular}
\end{tcolorbox}

% Section: Skills
% ------------------------------------------------------------------------------

\section*{Skills}

\begin{multicols}{2}
  \raggedright

  \subsection*{Most Recent and Familiar}

  \textbf{Languages}: Python, Bash, Lisp

  \textbf{Other}: Kubernetes, Git, Docker, AWS, Azure, Terraform

  \subsection*{Worked with in the Past}

  \textbf{Languages}: Go, Javascript, Haskell, Rust, Java, \LaTeX, C, \CC,
  MATLAB/Octave, CSS/LESS/SASS, SQL

  \textbf{Other}: Ansible, Packer, Webpack

  \vfill
  \columnbreak

\end{multicols}

% Section: Experience
% ------------------------------------------------------------------------------

\section*{Experience}

\subsection*{Cloud Engineer at IronNet \hfill March 2019 -- Present}

I am a member of the \textbf{\textsl{Cloud Infrastructure}} team at IronNet; our
team oversees cloud-related endeavors and also develops internal tooling. Some
things that I personally worked on:

\begin{itemize}
\item Designed and implemented a new data-ingest pipeline that leverages AWS
  managed services (like ALB, Kinesis, and ECS) in order to be more scalable and
  reliable than previous designs (for background: IronNet's flagship product
  ingests \textit{a lot} of data from customers).
\item Created and improved automation for managing Kubernetes clusters and
  IronNet's applications running on Kubernetes.
\item Created an internal tool (API and a corresponding CLI) leveraging IXIA
  BreakingPoint to send generated network traffic to various endpoints for
  testing things.
\item Helped to debug and fix various issues in internal deployments of Jenkins
  and Harbor, as well as in various internal applications that our team managed
  (e.g. for creating AWS accounts, managing cross-account permissions, or
  generating network data for testing).
\item Worked on getting IronNet's flagship product running in Azure.
\end{itemize}

\tag{Python} \tag{Go} \tag{Bash} \tag{Kubernetes} \tag{helm} \tag{AWS}
\tag{Azure} \tag{Terraform}

\subsection*{QA Engineer at Fugue \hfill Jul 2015 -- Jan 2019}

The QA team was in charge of designing and implementing a test harness for Fugue
(which was a platform for defining, creating, and monitoring infrastructure in
AWS and Azure). I created much of this system, as well as a variety of
general-purpose internal tooling.

\begin{itemize}
\item Helped design and create an end-to-end test harness for Fugue (Python,
  Bash, Go)
\item Wrote a utility for completely clearing AWS accounts (Python)
\item Created an automated pipeline for building test VMs in AWS and Azure
  (Ansible, Packer, Go, Azure Resource Manager)
\item Created CI builds in Travis and Concourse
\item Devised a literate-programming approach for running and documenting tests
\end{itemize}

\tag{Python} \tag{Bash} \tag{Clojure} \tag{Go} \tag{Haskell} \tag{AWS}
\tag{Azure} \tag{Ansible} \tag{Packer} \tag{Concourse}

\subsection*{Web Developer at Wells Fargo \hfill Feb 2015 -- Jul 2015}

Member of a small team creating an internal auditing and task-tracking
application.

\tag{Java} \tag{Spring} \tag{Hibernate} \tag{YUI} \tag{Javascript}

\subsection*{Startup Entrepreneur \hfill May 2014 -- Jan 2015}

Primarily focused on two business ventures:

\begin{itemize}
\item Partnered with a small team building a recruiting platform for
  high-level executives.

\item Worked with a medical clinic to create a multi-user web application for
  maintaining an audit trail of communications between doctors, patients,
  nurses, and call centers.
\end{itemize}

\tag{MEAN stack} \tag{Docker} \tag{Java 8} \tag{Scala} \tag{MySQL} \tag{Bash}
\tag{\LaTeX}

\subsection*{Consultant at Red Hat \hfill Aug 2011 -- May 2014}

As a consultant, I traveled to client sites and worked on a variety of projects
that Red Hat was involved with. Mostly, this involved integrating the JBoss
suite of products which Red Hat had recently acquired.

\begin{itemize}
\item \textit{GEICO} -- Helped to build and expand web services. Also helped to
  create an internal error tracking and aggregation platform using Grails and
  AngularJS.

\item \textit{Cigna} -- Worked on an application for inferring customer
  information using a rules engine.

\item \textit{Kohl's} -- Sole developer porting the main website to a website
  for kiosk machines.

\end{itemize}

\tag{Java} \tag{JBoss} \tag{JBoss Rules} \tag{jBPM} \tag{Hibernate}
\tag{MyBatis} \tag{Grails} \tag{AngularJS}

% Section: Education
% ------------------------------------------------------------------------------

\section*{Education}

\textsc{University of Virginia}, School of Engineering and Applied Science,
Charlottesville, VA \\
\textit{B.S. in Computer Science, May 2011}

% Section: Outside of Work
% ------------------------------------------------------------------------------

\section*{Outside of Work}

I enjoy family time, baby time, reading, learning, and playing sports, espcially
with other people.

\begin{itemize}
\item I like playing around with Emacs and Elisp
\item I try to help with IT-related tasks at my wife's law firm
\item President of my HOA
\item I love doing any kind of sports
\end{itemize}

\end{document}
